---
title: "Data cleaning V2"
output: html_document
date: "2024-05-13"
Author: Léa Cavalli
---

# Set up environment
```{r}
# Clean environment
rm( list = ls() )

# load necessary libraries
library(tidyverse)

# Load data
setwd("~/GitHub/Calibration-Review")
raw_data <- read.csv("review_396964_20240522013142.csv")
```

# Correct country inconsistencies
```{r}
# Explore country names 
raw_data |> 
  group_by(Study.setting) |>
  summarise(N=n())|>
  arrange(-N)
# install.packages("countries")
library(countries)
list_countries <- list_countries(nomenclature = "name_en")
raw_data |> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting)


# Correcting some inconsistencies
raw_data_V2 <- raw_data |>
  mutate(Study.setting = ifelse(Study.setting %in% c("United States", "USA"), "United States of America", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("eSwatini ", "Swaziland"), "Eswatini", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("UK"), "United Kingdom", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("Russia"), "Russian Federation", Study.setting))|>
  mutate(Study.setting = str_replace(Study.setting, ", and ", ", "))|>
  mutate(Study.setting = str_replace(Study.setting, "and ", ", "))|>
  mutate(Study.setting = gsub(";", ",", Study.setting))|>
  mutate(Study.setting = gsub(" \n", ", ", Study.setting))|>
  mutate(Study.setting = gsub("\n", ", ", Study.setting))|>
  mutate(Study.setting = gsub(",,", ",", Study.setting))
# still: # South Korea vs Democratic People's Republic of Korea vs DPR Korea
# change ; for , 
# change "/n" for ","


unique(raw_data_V2|> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting))


# Outliers 
raw_data_V2|> 
  filter(Study.setting %in% c("105 LMICs", "Southeast Asia", "sub-Saharan Africa", "Sub-Saharan Africa", "Not reported", ""))


# 3251: Study.setting = "105 LMICs"
# 1140: Study.setting = "Southeast Asia
# 1099: Study.setting = "sub-Saharan Africa"
# 2404 : Study.setting = "Not reported"
# 2007 : Study.setting = ""
# 1159: Study.setting = "Sub-Saharan Africa"

```


# Correct known option inconsistencies

```{r}
# Correct
raw_data_V3 <- raw_data_V2  |> 
  mutate(External.beliefs.or.evidence = ifelse(External.beliefs.or.evidence== "Other: No prior knowledge is incorporated for parameters to be calibrated.", "No prior knowledge is incorporated for parameters to be calibrated. ", External.beliefs.or.evidence))|>
    mutate(How.many.calibration.targets.were.used.for.estimation. = ifelse(How.many.calibration.targets.were.used.for.estimation.== "Other: Single", "Single ", How.many.calibration.targets.were.used.for.estimation.))|>
  mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Other", "Other ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Data likelihood", "Data likelihood ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Nature.of.calibration.results = ifelse(Nature.of.calibration.results== "Other: Sample estimate", "Sample estimate (multiple parameter sets)", Nature.of.calibration.results))|>
    mutate(Stochasticity.in.model = ifelse(Stochasticity.in.model== "Other: Stochastic", "Stochastic model ", Stochasticity.in.model))|>
    mutate(Name.of.calibration.algorithm = ifelse(Name.of.calibration.algorithm== "Other: Other", "Other ", Name.of.calibration.algorithm))

```



# Investigate new option inconsistencies

```{r}
raw_data_V3

# 0.1 Year published 
table(raw_data_V3$Year.published)

# 0.2 Disease type 
table(raw_data_V3$Disease.type..choose.all.that.apply.)

# 0.3 Model type 
table(raw_data_V3$Model.type)

# 0.4 Stochasticity in model 
table(raw_data_V3$Stochasticity.in.model)

# A.1 Scientific problem being solved (what is the purpose of calibration?) 
table(raw_data_V3$Scientific.problem.being.solved)

# B.1.1. Beliefs or evidence
table(raw_data_V3$External.beliefs.or.evidence)

# B.1.2. Choice of parameters to calibrate
table(raw_data_V3$Choice.of.parameters.to.calibrate)

# B.1.3. What justification was provided for choice of parameters to calibrate? Only for studies which calibrated a subset of parameters.
table(raw_data_V3$What.justification.was.provided.for.choice.of.parameters.to.calibrate.)
raw_data_V3  |> 
  filter(What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="Parameters are relevant to question of interest.; Other")|> 
  pull(Covidence..)
# 1285 : Ruchita

# B.1.4. How many parameters were calibrated?
table(raw_data_V3$How.many.parameters.were.calibrated.)

# B.2.2. Resolution of data used for defining calibration targets
table(raw_data_V3$Resolution.of.data..used.for.defining.calibration.targets)

#  B.2.3.  How many calibration targets were used for estimation?
table(raw_data_V3$How.many.calibration.targets.were.used.for.estimation.)

# C.1. Number of steps 
table(raw_data_V3$Number.of.steps..single.or.sequential.)

# C.2. Name of calibration algorithm 
table(raw_data_V3$Name.of.calibration.algorithm)

# C.3. Is calibration implementation (code) available in an open-access repository? 
table(raw_data_V3$Is.calibration.implementation..code..available.in.an.open.access.repository.)

# C.4. Goodness-of-fit (GOF) measure employed within calibration algorithm
table(raw_data_V3$Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm)

# C.5. What programming language was used for calibration?
table(raw_data_V3$What.programming.language.was.used.for.calibration.)

# C.6. Do authors list any programming packages used for calibration?
table(raw_data_V3$Do.authors.list.any.programming.packages.used.for.calibration.)

# D.1. Nature of calibration results
table(raw_data_V3$Nature.of.calibration.results)

# D.2. How are calibration results reported? 
table(raw_data_V3$How.are.calibration.results.reported.)

# D.3. How is uncertainty in calibration outputs reported? 
table(raw_data_V3$How.is.uncertainty.in.calibration.outputs.reported.)
raw_data_V3  |> 
  filter(How.is.uncertainty.in.calibration.outputs.reported. =="Uncertainty in calibration outputs is not reported.; Other ")|> 
  pull(Covidence..)
# 1247 : Multiple calibration

# D.4. What is the size of the calibration output? 
table(raw_data_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        pull(size.of.the.calibration.output.reported))

# If number provided, what is the range of the reported size? 
raw_data_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        filter(size.of.the.calibration.output.reported != "Not reported")|>
        pull(What.is.the.size.of.the.calibration.output.)

```
# Create clean data file for analysis
```{r}
# write.csv(raw_data_V3, "Clean_data_review.csv", row.names = F)

```


List of things that still need reviewing: 


Ruchita: 
  # 1285 : What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="Parameters are relevant to question of interest.; Other"


# 3251: Study.setting = "105 LMICs" - Ruchita 
# 1140: Study.setting = "Southeast Asia" - Lea 
# 1099: Study.setting = "sub-Saharan Africa" - Ruchita
# 2404 : Study.setting = "Not reported" - Ruchita
# 2007 : Study.setting = "" - Ruchita
# 1159: Study.setting = "Sub-Saharan Africa" - Lea 
