---
title: "Data cleaning V2"
output: html_document
date: "2024-05-13"
Author: Léa Cavalli
---

# Set up environment
```{r}
# Clean environment
rm( list = ls() )

# load necessary libraries
library(tidyverse)
library(xlsx)

# Load covidence raw data
setwd("~/GitHub/Calibration-Review")
Covidence_raw_data <- read.csv("Covidence_raw_data.csv")

# Load multiple calibrations data
Multiple_Calibration_data <- read.xlsx("Multiple_Calibration_data.xlsx", sheetName = "Sheet1")
colnames(Multiple_Calibration_data) <- Multiple_Calibration_data[2,]
Multiple_Calibration_data  <- Multiple_Calibration_data[-c(1:2),]

# Remove multiple calibration paper from covidence raw data 
Covidence_raw_data_1cal <- Covidence_raw_data |>
  filter(!(Covidence.. %in% Multiple_Calibration_data$`Covidence ID`)) 
```

# Correct country inconsistencies
```{r}
# Explore country names 
Covidence_raw_data_1cal |> 
  group_by(Study.setting) |>
  summarise(N=n())|>
  arrange(-N)
# install.packages("countries")
library(countries)
list_countries <- list_countries(nomenclature = "name_en")
Covidence_raw_data_1cal |> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting)


# Correcting some inconsistencies
Covidence_raw_data_1cal_V2 <- Covidence_raw_data_1cal |>
  mutate(Study.setting = ifelse(Study.setting %in% c("United States", "USA"), "United States of America", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("eSwatini ", "Swaziland"), "Eswatini", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("UK"), "United Kingdom", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("Russia"), "Russian Federation", Study.setting))|>
  mutate(Study.setting = str_replace(Study.setting, ", and ", ", "))|>
  mutate(Study.setting = str_replace(Study.setting, "and ", ", "))|>
  mutate(Study.setting = gsub(";", ",", Study.setting))|>
  mutate(Study.setting = gsub(" \n", ", ", Study.setting))|>
  mutate(Study.setting = gsub("\n", ", ", Study.setting))|>
  mutate(Study.setting = gsub(",,", ",", Study.setting))
# still: # South Korea vs Democratic People's Republic of Korea vs DPR Korea
# change ; for , 
# change "/n" for ","


unique(Covidence_raw_data_1cal_V2|> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting))


# Outliers 
Covidence_raw_data_1cal_V2|> filter(Study.setting == "41 sub-Saharan Africa countries")|> pull(Covidence..)
Covidence_raw_data_1cal_V2|> filter(Study.setting == "")|> pull(Covidence..)
Covidence_raw_data_1cal_V2|> filter(Study.setting == "Southeast Asia")|> pull(Covidence..)
Covidence_raw_data_1cal_V2|> filter(Study.setting == "sub-Saharan Africa")|> pull(Covidence..)
Covidence_raw_data_1cal_V2|> filter(Study.setting == "Sub-Saharan Africa")|> pull(Covidence..)
Covidence_raw_data_1cal_V2|> filter(Study.setting == "South-East Asia region, East Mediterranean region, South , North America region")|> pull(Covidence..)

```


# Correct known option inconsistencies
```{r}
# Correct
Covidence_raw_data_1cal_V3 <- Covidence_raw_data_1cal_V2  |> 
  mutate(External.beliefs.or.evidence = ifelse(External.beliefs.or.evidence== "Other: No prior knowledge is incorporated for parameters to be calibrated.", "No prior knowledge is incorporated for parameters to be calibrated. ", External.beliefs.or.evidence))|>
    mutate(How.many.calibration.targets.were.used.for.estimation. = ifelse(How.many.calibration.targets.were.used.for.estimation.== "Other: Single", "Single ", How.many.calibration.targets.were.used.for.estimation.))|>
  mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Other", "Other ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Data likelihood", "Data likelihood ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Nature.of.calibration.results = ifelse(Nature.of.calibration.results== "Other: Sample estimate", "Sample estimate (multiple parameter sets)", Nature.of.calibration.results))|>
    mutate(Stochasticity.in.model = ifelse(Stochasticity.in.model== "Other: Stochastic", "Stochastic model ", Stochasticity.in.model))|>
    mutate(Name.of.calibration.algorithm = ifelse(Name.of.calibration.algorithm== "Other: Other", "Other ", Name.of.calibration.algorithm))|>
    mutate(Model.type = ifelse(Model.type== "Other: Individual-based", "Individual-based ", Model.type))|>
    mutate(How.many.parameters.were.calibrated. = ifelse(How.many.parameters.were.calibrated.== "Other: Single", "Single ", How.many.parameters.were.calibrated.))|>
    mutate(How.many.calibration.targets.were.used.for.estimation. = ifelse(How.many.calibration.targets.were.used.for.estimation.== "Other: Multiple", "Multiple ", How.many.calibration.targets.were.used.for.estimation.))|>
    mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Ad-Hoc Distance", "Ad-hoc distance function (as in Approximate Bayesian Computation or least squares)", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Nature.of.calibration.results = ifelse(Nature.of.calibration.results== "Other: Point estimate", "Point estimate (single parameter / parameter set)", Nature.of.calibration.results))|>
    mutate(Number.of.steps..single.or.sequential. = ifelse(Number.of.steps..single.or.sequential.== "Other: \nNot reported", "Not reported", Number.of.steps..single.or.sequential.))|>
    mutate(Name.of.calibration.algorithm = ifelse(Name.of.calibration.algorithm== "Other: Not reported ", "Not reported", Name.of.calibration.algorithm))
```



# Investigate new option inconsistencies
```{r}
# 0.1 Year published 
table(Covidence_raw_data_1cal_V3$Year.published)

# 0.2 Disease type 
table(Covidence_raw_data_1cal_V3$Disease.type..choose.all.that.apply.)

# 0.3 Model type 
table(Covidence_raw_data_1cal_V3$Model.type)

# 0.4 Stochasticity in model 
table(Covidence_raw_data_1cal_V3$Stochasticity.in.model)

Covidence_raw_data_1cal_V3  |> 
  filter(Stochasticity.in.model =="Other: Both deterministic and stochastic ")|> 
  pull(Covidence..)
# 2710: Stochasticity.in.model =="Other: Both deterministic and stochastic " Yunfei Li


# A.1 Scientific problem being solved (what is the purpose of calibration?) 
table(Covidence_raw_data_1cal_V3$Scientific.problem.being.solved)
Covidence_raw_data_1cal_V3  |> 
  filter(Scientific.problem.being.solved =="")|> 
  pull(Covidence..)
# 1071: Scientific.problem.being.solved ==""  - Yunfei

# B.1.1. Beliefs or evidence
table(Covidence_raw_data_1cal_V3$External.beliefs.or.evidence)
Covidence_raw_data_1cal_V3  |> 
  filter(External.beliefs.or.evidence =="")|> 
  pull(Covidence..)
# 2966:External.beliefs.or.evidence =="" - Yunfei 
# 2243: External.beliefs.or.evidence =="" - Yunfei 
# 1628: External.beliefs.or.evidence =="" - Yunfei 
# 660: External.beliefs.or.evidence ==""  - Yunfei 

# B.1.2. Choice of parameters to calibrate
table(Covidence_raw_data_1cal_V3$Choice.of.parameters.to.calibrate)
Covidence_raw_data_1cal_V3  |> 
  filter(Choice.of.parameters.to.calibrate =="")|> 
  pull(Covidence..)
# 2243: Choice.of.parameters.to.calibrate =="" - Yunfei

# B.1.3. What justification was provided for choice of parameters to calibrate? Only for studies which calibrated a subset of parameters.
table(Covidence_raw_data_1cal_V3$What.justification.was.provided.for.choice.of.parameters.to.calibrate.)
Covidence_raw_data_1cal_V3  |> 
  filter(What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="")|> 
  pull(Covidence..)
# 1990: What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="" - Yunfei

# B.1.4. How many parameters were calibrated?
table(Covidence_raw_data_1cal_V3$How.many.parameters.were.calibrated.)


# B.2.2. Resolution of data used for defining calibration targets
table(Covidence_raw_data_1cal_V3$Resolution.of.data..used.for.defining.calibration.targets)

#  B.2.3.  How many calibration targets were used for estimation?
table(Covidence_raw_data_1cal_V3$How.many.calibration.targets.were.used.for.estimation.)

# C.1. Number of steps 
table(Covidence_raw_data_1cal_V3$Number.of.steps..single.or.sequential.)

# C.2. Name of calibration algorithm 
table(Covidence_raw_data_1cal_V3$Name.of.calibration.algorithm)
Covidence_raw_data_1cal_V3  |> 
  filter(Name.of.calibration.algorithm =="Other: ")|> 
  pull(Covidence..)
# 842: Name.of.calibration.algorithm was left empty- Ruchita Balasubramanian

# C.3. Is calibration implementation (code) available in an open-access repository? 
table(Covidence_raw_data_1cal_V3$Is.calibration.implementation..code..available.in.an.open.access.repository.)

# C.4. Goodness-of-fit (GOF) measure employed within calibration algorithm
table(Covidence_raw_data_1cal_V3$Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm)
Covidence_raw_data_1cal_V3  |> 
  filter(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm =="Other: ")|> 
  pull(Covidence..)
# 1333: Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm was left empty- Yunfei

# C.5. What programming language was used for calibration?
table(Covidence_raw_data_1cal_V3$What.programming.language.was.used.for.calibration.)

# C.6. Do authors list any programming packages used for calibration?
table(Covidence_raw_data_1cal_V3$Do.authors.list.any.programming.packages.used.for.calibration.)
Covidence_raw_data_1cal_V3  |> 
  filter(Do.authors.list.any.programming.packages.used.for.calibration. =="Other: ")|> 
  pull(Covidence..)
# 1333: Do.authors.list.any.programming.packages.used.for.calibration. was left empty - Yunfei

# D.1. Nature of calibration results
table(Covidence_raw_data_1cal_V3$Nature.of.calibration.results)

# D.2. How are calibration results reported? 
table(Covidence_raw_data_1cal_V3$How.are.calibration.results.reported.)

# D.3. How is uncertainty in calibration outputs reported? 
table(Covidence_raw_data_1cal_V3$How.is.uncertainty.in.calibration.outputs.reported.)

# D.4. What is the size of the calibration output? 
table(Covidence_raw_data_1cal_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        pull(size.of.the.calibration.output.reported))

# If number provided, what is the range of the reported size? 
Covidence_raw_data_1cal_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        filter(size.of.the.calibration.output.reported != "Not reported")|>
        pull(What.is.the.size.of.the.calibration.output.)

```

List of things that still need reviewing: 

Lea
# 1159: Study.setting = "Sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "Sub-Saharan Africa (Country names not reported)".

Ruchita:
# 842: Name.of.calibration.algorithm was left empty.
# 842  Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.
# 2404: Study.setting = "" - Is it possibly to provide a list of country names ? If not, please change it to "Not reported".
# 1027 : Study.setting = "sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "sub-Saharan Africa (Country names not reported)".
# 1254 Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.

Yunfei : 
# 2710: Stochasticity.in.model is set to "Both deterministic and stochastic ". - Could you please provide a short explanation for this statement. Are there several models in the study ? Or is one model used for calibration and its equivalent used for simulation ? or other.
# 2966:External.beliefs.or.evidence was left empty.
# 2243: External.beliefs.or.evidence was left empty. 
# 2243: Choice.of.parameters.to.calibrate was left empty.
# 1628: External.beliefs.or.evidence was left empty.
# 660: External.beliefs.or.evidence was left empty.
# 1990: What.justification.was.provided.for.choice.of.parameters.to.calibrate. was left empty.
# 1333: Do.authors.list.any.programming.packages.used.for.calibration. was left empty.
# 1333: Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm was left empty.
#1239 Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.
# 2214: Study.setting = "41 sub-Saharan Africa countries" - Is it possibly to provide a list of country names ? If not, please change it to "41 sub-Saharan Africa countries (Country names not reported)".
# 2193: Study.setting = "Sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "Sub-Saharan Africa (Country names not reported)".
# 1995 : Study.setting = "Sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "Sub-Saharan Africa (Country names not reported)".
# 1722: Study.setting = "Sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "Sub-Saharan Africa (Country names not reported)".
# 831: Study.setting = "South-East Asia region, East Mediterranean region, South , North America region" - Is it possibly to provide a list of country names ? If not, please change it to "South-East Asia region, East Mediterranean region, South , North America region (Country names not reported)".

Emmanuelle
#2046: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.

# Clean Column names
```{r}
Covidence_raw_data_1cal_V3 <- Covidence_raw_data_1cal_V3 |> rename("Covidence.ID" = "Covidence..")
colnames(Covidence_raw_data_1cal_V3)[which(grepl("Other",colnames(Covidence_raw_data_1cal_V3)))] <- paste("Other_", colnames(Covidence_raw_data_1cal_V3)[which(grepl("Other",colnames(Covidence_raw_data_1cal_V3)))-1], sep="" )
colnames(Covidence_raw_data_1cal_V3)[which(grepl("Other",colnames(Covidence_raw_data_1cal_V3)))][5] <- paste("Other_", colnames(Covidence_raw_data_1cal_V3)[which(grepl("Other",colnames(Covidence_raw_data_1cal_V3)))[5]-2], sep="" )
colnames(Covidence_raw_data_1cal_V3)[which(grepl("clear",colnames(Covidence_raw_data_1cal_V3)))] <- paste("Not_Clear_", colnames(Covidence_raw_data_1cal_V3)[which(grepl("Other",colnames(Covidence_raw_data_1cal_V3)))[5]-2], sep="" )
```

# Clean "Other" algorithm names
```{r}
# Make vectors containing all versions of each algorithm's name
ABC_SMC_names <- c("Approximate Bayesian Computation Sequential Monte Carlo scheme", 
                   "Approximate Bayesian computation with sequential Monte Carlo sampling", 
                   "Approximate Bayesian Computation with Sequential Monte Carlo Sampling", 
                   "Aproximate Bayesian Computation Sequential Monte Carlo (ABC-SMC) algorithm ", 
                   "Approximate Bayesian Computation Sequential Monte Carlo (ABC SMC) method", 
                   "Approximate Bayesian Computation with Sequential Monte Carlo sampling (ABC-SMC) method")
HME_names <- c("History matching with emulation", 
               "history matching with model emulation", 
               "history matching with emulation", 
               " history matching with emulation")
IMIS_names <- c("incremental mixture importance sampling", 
                   "Incremental mixture importance sampling", 
                   "Incremental Mixture Importance Sampling", 
                " Incremental Mixture Importance Sampling", 
                   "incremental mixture importance sampling (IMIS)", 
                   "Incremental Mixture Importance Sampling (IMIS) ",
                   "a Bayesian framework with incremental mixture importance sampling", 
                   "Incremental Mixture Importance Sampling")
MCF_names <- c("Monte-Carlo filtering", 
                   "Monte-Carlo filtering ", 
                   "Monte Carlo filtering")
BM_names <- c("Bayesian melding",
              " Bayesian melding")
NM_names <- c("Iterative, directed-search Nelder-Mead (NM) method", 
                   "Nelder-Mead algorithm ", 
              "Nelder-Mead")
SIR_names <- c("sample-importance-resampling ", 
               "Sampling importance resampling ",
               "Sampling Importance Resampling",
               "Semi-Bayesian Sampling/Importance-Resampling algorithm", 
               "Sampling-importance-resampling (SIR) approach")
SMC_PF_names <- c("sequential Monte Carlo method based on particle filtering", 
                   "sequential Monte Carlo method based on particle filtering",
                   "particle Markov\nchain Monte Carlo (PMCMC",
                   "Sequential Monte Carlo method based on particle filtering known as\nMIF for Likelihood Maximization by Iterated Filtering")
PSPO_names <- c("parallel simultaneous perturbation \noptimisation (PSPO)",
"parallel simultaneous perturbation optimization ")

# Recode the Other algorithm names with standardized name 
Covidence_raw_data_1cal_v4 <- Covidence_raw_data_1cal_V3 |>
  mutate(Other_Name.of.calibration.algorithm_V2= ifelse(Other_Name.of.calibration.algorithm %in% ABC_SMC_names, "Aproximate Bayesian Computation Sequential Monte Carlo (ABC-SMC)", 
                         ifelse(Other_Name.of.calibration.algorithm %in% HME_names, "History matching with emulation",
                                ifelse(Other_Name.of.calibration.algorithm %in% IMIS_names, "Incremental Mixture Importance Sampling (IMIS)", 
                                       ifelse(Other_Name.of.calibration.algorithm %in% MCF_names, "Monte-Carlo filtering", 
                                              ifelse(Other_Name.of.calibration.algorithm %in% SIR_names, "Sampling importance resampling", 
                                                     ifelse(Other_Name.of.calibration.algorithm %in% SMC_PF_names, "Sequential Monte Carlo method based on particle filtering", 
                                                            ifelse(Other_Name.of.calibration.algorithm %in% BM_names, "Bayesian melding", 
                                                                   ifelse(Other_Name.of.calibration.algorithm %in% NM_names, "Nelder-Mead algorithm", 
                                                                          ifelse(Other_Name.of.calibration.algorithm %in% PSPO_names, "Parallel Simultaneous perturbation Optimisation (PSPO)", Other_Name.of.calibration.algorithm))))))))))
```

```{r}
# Among those that fall into pre-defined calibration algorithm, 
# Are there any with information in "Other" as well ? 
table(Covidence_raw_data_1cal_v4 |>
  filter(Name.of.calibration.algorithm != "Other ") |>
  pull(Other_Name.of.calibration.algorithm))
# yes, which ? 
Covidence_raw_data_1cal_v4 |>
  filter(Name.of.calibration.algorithm != "Other ", 
         Other_Name.of.calibration.algorithm != "") |>
  pull(Covidence.ID)

# Among those that do not fall into pre-defined calibration algorithm, 
# Which are the main other categories ? 
Covidence_raw_data_1cal_v4 |>
  filter(Name.of.calibration.algorithm == "Other ")|>
  group_by(Other_Name.of.calibration.algorithm_V2) |>
  summarise(N=n())  |>
  arrange(-N)

# write.csv(Covidence_raw_data_1cal_v4 |> select(Covidence.ID, Study.ID, Name.of.calibration.algorithm, Other_Name.of.calibration.algorithm, Other_Name.of.calibration.algorithm_V2), "Data_Calibration_Algorithm.csv", row.names = F)
```

# Create clean data file for analysis
```{r}
# write.csv(Covidence_raw_data_1cal_v4, "Clean_data_review.csv", row.names = F)
```


