---
title: "Data cleaning V2"
output: html_document
date: "2024-05-13"
Author: Léa Cavalli
---

# Set up environment
```{r}
# Clean environment
rm( list = ls() )

# load necessary libraries
library(tidyverse)

# Load data
setwd("~/GitHub/Calibration-Review")
raw_data <- read.csv("review_396964_20240608035120.csv")
```

# Correct country inconsistencies
```{r}
# Explore country names 
raw_data |> 
  group_by(Study.setting) |>
  summarise(N=n())|>
  arrange(-N)
# install.packages("countries")
library(countries)
list_countries <- list_countries(nomenclature = "name_en")
raw_data |> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting)


# Correcting some inconsistencies
raw_data_V2 <- raw_data |>
  mutate(Study.setting = ifelse(Study.setting %in% c("United States", "USA"), "United States of America", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("eSwatini ", "Swaziland"), "Eswatini", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("UK"), "United Kingdom", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("Russia"), "Russian Federation", Study.setting))|>
  mutate(Study.setting = str_replace(Study.setting, ", and ", ", "))|>
  mutate(Study.setting = str_replace(Study.setting, "and ", ", "))|>
  mutate(Study.setting = gsub(";", ",", Study.setting))|>
  mutate(Study.setting = gsub(" \n", ", ", Study.setting))|>
  mutate(Study.setting = gsub("\n", ", ", Study.setting))|>
  mutate(Study.setting = gsub(",,", ",", Study.setting))
# still: # South Korea vs Democratic People's Republic of Korea vs DPR Korea
# change ; for , 
# change "/n" for ","


unique(raw_data_V2|> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting))


# Outliers 
raw_data_V2|> 
  filter(Study.setting %in% c("105 LMICs", "Southeast Asia", "sub-Saharan Africa", "Sub-Saharan Africa", "Not reported", ""))


# 3251: Study.setting = "105 LMICs"
# 1140: Study.setting = "Southeast Asia
# 1099: Study.setting = "sub-Saharan Africa"
# 2404 : Study.setting = "Not reported"
# 2007 : Study.setting = ""
# 1159: Study.setting = "Sub-Saharan Africa"

```


# Correct known option inconsistencies

```{r}
# Correct
raw_data_V3 <- raw_data_V2  |> 
  mutate(External.beliefs.or.evidence = ifelse(External.beliefs.or.evidence== "Other: No prior knowledge is incorporated for parameters to be calibrated.", "No prior knowledge is incorporated for parameters to be calibrated. ", External.beliefs.or.evidence))|>
    mutate(How.many.calibration.targets.were.used.for.estimation. = ifelse(How.many.calibration.targets.were.used.for.estimation.== "Other: Single", "Single ", How.many.calibration.targets.were.used.for.estimation.))|>
  mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Other", "Other ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Data likelihood", "Data likelihood ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Nature.of.calibration.results = ifelse(Nature.of.calibration.results== "Other: Sample estimate", "Sample estimate (multiple parameter sets)", Nature.of.calibration.results))|>
    mutate(Stochasticity.in.model = ifelse(Stochasticity.in.model== "Other: Stochastic", "Stochastic model ", Stochasticity.in.model))|>
    mutate(Name.of.calibration.algorithm = ifelse(Name.of.calibration.algorithm== "Other: Other", "Other ", Name.of.calibration.algorithm))|>
    mutate(Model.type = ifelse(Model.type== "Other: Individual-based", "Individual-based ", Model.type))|>
    mutate(How.many.parameters.were.calibrated. = ifelse(How.many.parameters.were.calibrated.== "Other: Single", "Single ", How.many.parameters.were.calibrated.))|>
    mutate(How.many.calibration.targets.were.used.for.estimation. = ifelse(How.many.calibration.targets.were.used.for.estimation.== "Other: Multiple", "Multiple ", How.many.calibration.targets.were.used.for.estimation.))|>
    mutate(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm = ifelse(Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm== "Other: Ad-Hoc Distance", "Ad-hoc distance function (as in Approximate Bayesian Computation or least squares)", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))|>
    mutate(Nature.of.calibration.results = ifelse(Nature.of.calibration.results== "Other: Point estimate", "Point estimate (single parameter / parameter set)", Nature.of.calibration.results))


```



# Investigate new option inconsistencies

```{r}
# 0.1 Year published 
table(raw_data_V3$Year.published)

# 0.2 Disease type 
table(raw_data_V3$Disease.type..choose.all.that.apply.)

# 0.3 Model type 
table(raw_data_V3$Model.type)

# 0.4 Stochasticity in model 
table(raw_data_V3$Stochasticity.in.model)
raw_data_V3  |> 
  filter(Stochasticity.in.model =="Other: ")|> 
  pull(Covidence..)
# 35

# A.1 Scientific problem being solved (what is the purpose of calibration?) 
table(raw_data_V3$Scientific.problem.being.solved)

# B.1.1. Beliefs or evidence
table(raw_data_V3$External.beliefs.or.evidence)

# B.1.2. Choice of parameters to calibrate
table(raw_data_V3$Choice.of.parameters.to.calibrate)

# B.1.3. What justification was provided for choice of parameters to calibrate? Only for studies which calibrated a subset of parameters.
table(raw_data_V3$What.justification.was.provided.for.choice.of.parameters.to.calibrate.)
raw_data_V3  |> 
  filter(What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="Parameters are relevant to question of interest.; Other")|> 
  pull(Covidence..)
# 1285 : Ruchita

# B.1.4. How many parameters were calibrated?
table(raw_data_V3$How.many.parameters.were.calibrated.)

# B.2.2. Resolution of data used for defining calibration targets
table(raw_data_V3$Resolution.of.data..used.for.defining.calibration.targets)

#  B.2.3.  How many calibration targets were used for estimation?
table(raw_data_V3$How.many.calibration.targets.were.used.for.estimation.)

# C.1. Number of steps 
table(raw_data_V3$Number.of.steps..single.or.sequential.)

# C.2. Name of calibration algorithm 
table(raw_data_V3$Name.of.calibration.algorithm)

# C.3. Is calibration implementation (code) available in an open-access repository? 
table(raw_data_V3$Is.calibration.implementation..code..available.in.an.open.access.repository.)

# C.4. Goodness-of-fit (GOF) measure employed within calibration algorithm
table(raw_data_V3$Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm)


# C.5. What programming language was used for calibration?
table(raw_data_V3$What.programming.language.was.used.for.calibration.)

# C.6. Do authors list any programming packages used for calibration?
table(raw_data_V3$Do.authors.list.any.programming.packages.used.for.calibration.)

# D.1. Nature of calibration results
table(raw_data_V3$Nature.of.calibration.results)

# D.2. How are calibration results reported? 
table(raw_data_V3$How.are.calibration.results.reported.)

# D.3. How is uncertainty in calibration outputs reported? 
table(raw_data_V3$How.is.uncertainty.in.calibration.outputs.reported.)
raw_data_V3  |> 
  filter(How.is.uncertainty.in.calibration.outputs.reported. =="Uncertainty in calibration outputs is not reported.; Other ")|> 
  pull(Covidence..)
# 1247 : Multiple calibration

# D.4. What is the size of the calibration output? 
table(raw_data_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        pull(size.of.the.calibration.output.reported))

# If number provided, what is the range of the reported size? 
raw_data_V3  |> 
        mutate(size.of.the.calibration.output.reported = ifelse(What.is.the.size.of.the.calibration.output. == "Not reported", "Not reported", "[Number provided]"))|>
        filter(size.of.the.calibration.output.reported != "Not reported")|>
        pull(What.is.the.size.of.the.calibration.output.)

```


# Clean "Other" algorithm names
```{r}
# Recode 
ABC_SMC_names <- c("Approximate Bayesian Computation Sequential Monte Carlo scheme", 
                   "Approximate Bayesian computation with sequential Monte Carlo sampling", 
                   "Approximate Bayesian Computation with Sequential Monte Carlo Sampling", 
                   "Aproximate Bayesian Computation Sequential Monte Carlo (ABC-SMC) algorithm ")

HME_names <- c("History matching with emulation", 
               "history matching with model emulation", 
               "history matching with emulation", 
               " history matching with emulation")

IMIS_names <- c("incremental mixture importance sampling", 
                   "Incremental mixture importance sampling", 
                   "Incremental Mixture Importance Sampling", 
                " Incremental Mixture Importance Sampling", 
                   "incremental mixture importance sampling (IMIS)", 
                   "Incremental Mixture Importance Sampling (IMIS) ",
                   "a Bayesian framework with incremental mixture importance sampling", 
                   "Incremental Mixture Importance Sampling")

MCF_names <- c("Monte-Carlo filtering", 
                   "Monte-Carlo filtering ", 
                   "Monte Carlo filtering")


BM_names <- c("Bayesian melding",
              " Bayesian melding")

NM_names <- c("Iterative, directed-search Nelder-Mead (NM) method", 
                   "Nelder-Mead algorithm ")

SIR_names <- c("sample-importance-resampling ", 
               "Sampling importance resampling ",
               "Sampling Importance Resampling",
               "Semi-Bayesian Sampling/Importance-Resampling algorithm")

SMC_PF_names <- c("sequential Monte Carlo method based on particle filtering", 
                   "sequential Monte Carlo method based on particle filtering",
                   "Sampling Importance Resampling",
                   "Sequential Monte Carlo method based on particle filtering known as\nMIF for Likelihood Maximization by Iterated Filtering")

PSPO_names <- c("parallel simultaneous perturbation \noptimisation (PSPO)",
"parallel simultaneous perturbation optimization ")


raw_data_Calibration_Algorithm_other <- raw_data_V3 |>
  mutate(Other_V2= ifelse(X.Other..details..2 %in% ABC_SMC_names, "Aproximate Bayesian Computation Sequential Monte Carlo (ABC-SMC)", 
                         ifelse(X.Other..details..2 %in% HME_names, "History matching with emulation",
                                ifelse(X.Other..details..2 %in% IMIS_names, "Incremental Mixture Importance Sampling (IMIS)", 
                                       ifelse(X.Other..details..2 %in% MCF_names, "Monte-Carlo filtering", 
                                              ifelse(X.Other..details..2 %in% SIR_names, "Sampling importance resampling", 
                                                     ifelse(X.Other..details..2 %in% SMC_PF_names, "Sequential Monte Carlo method based on particle filtering", 
                                                            ifelse(X.Other..details..2 %in% BM_names, "Bayesian melding", 
                                                                   ifelse(X.Other..details..2 %in% NM_names, "Nelder-Mead algorithm", 
                                                                          ifelse(X.Other..details..2 %in% PSPO_names, "Parallel Simultaneous perturbation Optimisation (PSPO)", X.Other..details..2)))))))))) |>
  rename("Other" = "X.Other..details..2")


raw_data_Calibration_Algorithm_other_subset <- raw_data_Calibration_Algorithm_other |>
  select(Covidence.., Study.ID, Name.of.calibration.algorithm, Other, Other_V2)

# write.csv(raw_data_Calibration_Algorithm_other_subset, "Data_Calibration_Algorithm.csv", row.names = F)


raw_data_Calibration_Algorithm_other_subset |>
  filter(Name.of.calibration.algorithm != "Other ") |>
  filter(Other !="")|>
  pull(Covidence..)

raw_data_Calibration_Algorithm_other_subset |>
  group_by(Other_V2) |>
  summarise(N=n())  |>
  arrange(-N)
```


# Create clean data file for analysis
```{r}
# write.csv(raw_data_V3, "Clean_data_review.csv", row.names = F)

```


List of things that still need reviewing: 


# 1140: Study.setting = "Southeast Asia" - Lea 
# 1159: Study.setting = "Sub-Saharan Africa" - Lea 
# 1239: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. -  Yunfei Li 
# 805: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. -   Léa Cavalli

Ruchita Balasubramanian
# 1285 : What.justification.was.provided.for.choice.of.parameters.to.calibrate. =="Parameters are relevant to question of interest.; Other"
# 3251: Study.setting = "105 LMICs" - Is it possibly to provide a list of country names ? If not, please change it to "105 LMICs (Country names not reported)".
# 1099: Study.setting = "sub-Saharan Africa" - Is it possibly to provide a list of country names ? If not, please change it to "Sub-Saharan Africa (Country names not reported)".
# 2007 : Study.setting = ""  - Is it possibly to provide a list of country names ? If not, please change it to "Not reported".
# 2285: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section.- Please choose one or the other, or provide a reason why both are used.
# 2155: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 
# 2058: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 
# 1501: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 
# 1254: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.
# 3251: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.   
# 1227: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 
# 1185: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used.  
# 883: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 
# 842: Has both a calibration name selected in "Name of Calibration Algorithm", and information input in the "Other" section. - Please choose one or the other, or provide a reason why both are used. 