---
title: "Objective 1"
output: html_document
date: "2024-05-04"
Author: Léa Cavalli
---

# Set up environment
```{r}
# Clean environment
rm( list = ls() )

# load necessary libraries
library(tidyverse)

# Load data
setwd("~/GitHub/Calibration-Review")
raw_data <- read.csv("review_396964_20240504214514.csv")
```

# Correct country inconsistencies
```{r}
# Explore country names 
raw_data |> 
  group_by(Study.setting) |>
  summarise(N=n())|>
  arrange(-N)
# install.packages("countries")
library(countries)
list_countries <- list_countries(nomenclature = "name_en")
raw_data |> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting)


# Correcting some inconsistencies
raw_data_V2 <- raw_data |>
  mutate(Study.setting = ifelse(Study.setting %in% c("United States", "USA"), "United States of America", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("eSwatini ", "Swaziland"), "Eswatini", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("UK"), "United Kingdom", Study.setting))|>
  mutate(Study.setting = ifelse(Study.setting %in% c("Russia"), "Russian Federation", Study.setting))|>
  mutate(Study.setting = str_replace(Study.setting, ", and ", ", "))|>
  mutate(Study.setting = str_replace(Study.setting, "and ", ", "))
# still: # South Korea vs Democratic People's Republic of Korea

unique(raw_data_V2|> 
  filter(! Study.setting %in% list_countries) |> 
  pull(Study.setting))


# Outliers 
raw_data_V2|> 
  filter(Study.setting %in% c("105 LMICs", "Southeast Asia", "sub-Saharan Africa", "Not reported"))

# 3251: Study.setting = "105 LMICs"
# 1140: Study.setting = "Southeast Asia
# 1099: Study.setting = "sub-Saharan Africa"
# 994: Study.setting = "Not reported"

```



# Investigate outliers 
```{r}
# Data cleaning 
# remove those that have multiple calibration ?
# size of calibration output: commas, no commas
# Outliers

raw_data  |> 
  filter(How.many.parameters.were.calibrated. =="")
# 351 :  How.many.parameters.were.calibrated. is empty

raw_data  |> 
  filter(How.many.calibration.targets.were.used.for.estimation. =="Other: Single")
# 1960 :  How.many.calibration.targets.were.used.for.estimation. is set to "Other: Single"

raw_data  |> 
  filter(grepl("Other: ", Name.of.calibration.algorithm))
# 3216 : Other: Method of moments	
# 894 :  Other: Latin Hypercube Sampling	

raw_data  |> 
  filter(grepl("Other: ", Goodness.of.fit..GOF..measure.employed.within.calibration.algorithm))
# 2366: Other: Other	
# 805: Other: Data likelihood	

raw_data |> 
    filter(grepl("Other", Nature.of.calibration.results))
# 845: Multiple calibration

raw_data  |> 
  filter(External.beliefs.or.evidence =="")
# 1227: External.beliefs.or.evidence is empty


raw_data |> 
    filter(grepl("Other", External.beliefs.or.evidence))
# 2293 : Other: No prior knowledge is incorporated for parameters to be calibrated.	
# 1279 : Other: No prior knowledge is incorporated for parameters to be calibrated.	


raw_data  |> 
  filter(How.are.calibration.results.reported. == "Numerical: e.g. as value(s).; Calibration results are not reported. ")
# 789: How.are.calibration.results.reported. == "Numerical: e.g. as value(s).; Calibration results are not reported. "

raw_data  |> 
  filter(How.is.uncertainty.in.calibration.outputs.reported. == "Graphical: As a plot; e.g., a line with shaded areas indicating uncertainty intervals ; Uncertainty in calibration outputs is not reported.")
# 1524 : How.is.uncertainty.in.calibration.outputs.reported. == "Graphical: As a plot; e.g., a line with shaded areas indicating uncertainty intervals ; Uncertainty in calibration outputs is not reported."

```



Comments: 
* Covidence automatically outputs the "Study ID" (i.e. Author name + year), and the Title of the papers 
* Country names have inconsistencies

Questions for data cleaning
* what do I do with those that have multiple calibrations ? Do I count each calibration as a separate article ?

Questions for Objective 1
* For any category where multiple choice selection was possible - what do we do when several options have been selected ? Do it add +1 count to each selected option ?
* For  D.4. (What is the size of the calibration output?), are you interested in the count + percentage of articles reporting the size of calibration output vs not ?
* Following  D.4., shall I  remove point estimates from the summary statistic of the range of calibration sizes ? Also, would it make sense to report the ranges of  calibration sizes separately for articles with sample estimate vs distribution estimate outputs ?


Questions for Objective 3:
* Is it normal that model type and stochasticity within "0. General" are not included in the PIPO framework ?
* Item 1 (A.1 Scientific problem being solved (what is the purpose of calibration?)) in "A. Purpose" category does not have a "Not reported" option. As such, it probably does not make sense to include it in PIPO ?
* Is it normal that "B.1.4. How many parameters were calibrated?" is not included in the PIPO framework ?
* For the category "C.4 Goodness-of-fit (GOF) measure employed within calibration algorithm", only the "Ad-hoc distance function (as in Approximate Bayesian Computation or least squares)" and "Data likelihood " options are listed in PIPO. Would you like me to consider all other possible options (i.e. "Not Reported", "not clear" and "Other") as not reported ? Specifically asking because I think the option "Other" could still be considered as Reported.
* Is it normal that programming language (i.e. C.5) and package name (i.e. C.5) are not included in PIPO ?

